---
title: "ADA Midterm Exam"
author: "Taylor Kaser"
date: "2022-10-13"
output: html_document
---

# ADA Midterm Exam

```{r}
# Load libraries
library(tidyverse)
library(readr)
library(table1)
```


## Question 3: Using the titanic dataset located at "https://github.com/kijohnson/Data",  prepare an R markdown file that shows the code for 
### a) importing the dataset

```{r}
# Load Titanic data

titanic_data <- read_csv("https://raw.githubusercontent.com/kijohnson/Data/main/titanic.csv")

# Examine data
summary(titanic_data)

# Change Survived, PClass, and Sex to factors
titanic_data_clean <- titanic_data %>%
  mutate(Survived = as.factor(Survived)) %>%
  mutate(Sex = as.factor(Sex)) %>%
  mutate(Pclass = as.factor(Pclass))
  
```

##b) determining the median age for by passenger class

```{r}
# Determine median age by Pclass using table1

table1(~ Age | Pclass, data = titanic_data_clean)

```

##c) a plot that shows medians, spread of data, and outliers for the continuous variable age according to passenger class. Report the medians by passenger class and upload a PDF or picture of your plot.

```{r}
# Create boxplot

titanic_data_clean %>%
  ggplot(aes(x = Pclass, y = Age)) + # Maps Pclass (x) and Age (y) onto the plot
  geom_boxplot() + # specifies the type of plot is a boxplot
  labs(x = "Passenger Class", y = "Age",  title = "Age by Passenger Class") + # Creates axis and labels and graph title
  theme_minimal() # Removes grey background

ggsave(filename = "Age_Pclass_bplot.png",
       width = 4, height = 4, units = "in", bg="white") # Saves boxplot as .png - stored in working directory

```

## Question 4

### a. Put the version of the code file that you wrote for question 3 that includes annotation for what each step does in a Github repository (you can use the one previously created in class or for your homework or create a new one).

### b. Next, add code to determine the percentage of males and females by class. Save this new version and push the new version to your Github repository.

```{r}
# Determine percentage of males/females by class using table1

table1(~ Sex | Pclass, data = titanic_data_clean)
```


### c. Provide a link to your Github repository containing the code file for review.




